Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
handles question about 'what are msre design models' .

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design calculations
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. 
The \gls{MSRE} design calculation in \cref{fig:temp_compare} was conducted in 
1963
32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
EQUIPOSE, and THERMOS). That calculation was conducted in two-dimensional R-Z 
geometry (a cylinder with angular symmetry), with 20 spatial regions. Notably, 
one limitation of the \gls{ORNL} model was the control rod thimbles that, due to 
angular symmetry, were effectively a cylindrical shell of metal.

>>>>

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design calculations
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. 
The \gls{ORNL} \gls{MSRE} design calculations, conducted in 
1963-1964,  were 32-group calculations using legacy computing tools (GAM-I, MODRIC, and 
EQUIPOSE, and THERMOS). Those calculations were conducted in two-dimensional R-Z 
geometry (a cylinder with angular symmetry), with 20 spatial regions. Notably, 
one limitation of the \gls{ORNL} model was the control rod thimbles that, due to 
angular symmetry, were effectively a cylindrical shell of metal.

### 2017-11-27 revise/revise.tex
handles description of the model from ORNL.
handles question about 'what are msre design models' .

\question The authors should briefly describe what ``MSRE design models'' are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
\begin{solution}
        The paper has been clarified. That section is now careful to state that 
        our comparison is made against the simple two-group calculation 
        conducted to pinpoint the design of the MSRE. 
\end{solution}

>>>>

\question The authors should briefly describe what ``MSRE design models'' are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
\begin{solution}
        The paper has been clarified. That section is now careful to state that 
        our comparison is made against a 1963-1964 calculation conducted by ORNL 
        to pinpoint the MSRE design. The text has been updated to refer to 
        ``MSRE design models'' as ``MSRE design calculations'' and explains 
        that the MSRE design calculations conducted in 1963 were 32-group 
        calculations using legacy computing tools (GAM-I, MODRIC, and EQUIPOSE, 
        and THERMOS). These calculations were conducted in two-dimensional R-Z 
        geometry (a cylinder with angular symmetry), with 20 spatial regions. 
        Notably, one limitation of the ORNL model was the control rod thimbles 
        that, due to angular symmetry, were effectively a cylindrical shell of 
        metal.  
\end{solution}
